A High-Order Discontinuous Galerkin Solver with Dynamic Adaptive Mesh Refinement to Simulate Cloud Formation Processes

### 2019-09-09 writing/slides/ppam.tex
Add 4:3 support for PPAM slides.

% https://tex.stackexchange.com/questions/123106/detect-aspect-ratio-in-beamer?noredirect=1&lq=1
\documentclass[aspectratio=169]{beamer}
%\documentclass[]{beamer}
%\usepackage{eulervm}
%\usetheme{metropolis} % Use metropolis theme
\usepackage[conference]{beamertheme_tumtalk} % headline and footline
\usepackage{beamercolorscheme_tum} % colorscheme
\usepackage{beamerfontthemestructurebold} % bold headings

@@

% \newcommand{\Qrho}{\ensuremath{\rho}}
% \newcommand{\Qj}{\ensuremath{\rho \bm{v}}}
% %\newcommand{\Qv}{\ensuremath{\Qrho^{-1} \Qj}}
% \newcommand{\Qv}{\ensuremath{\bm{v}}}
% \newcommand{\QE}{\ensuremath{\rho E}}
% \newcommand{\stressT}{\ensuremath{\bm{\sigma}}}
% \newcommand{\pressure}{\ensuremath{p}}
% \newcommand{\maxConvEigen}{\ensuremath{\vert \lambda_c^{\text{max}} \vert}}
% \newcommand{\maxViscEigen}{\ensuremath{\vert \lambda_v^{\text{max}} \vert}}

@@

\title[High-Order DG with Dynamic AMR to Simulate Clouds]{A High-Order Discontinuous Galerkin Solver with Dynamic Adaptive Mesh Refinement to Simulate Cloud Formation Processes}
\subtitle[PPAM]{PPAM 2019}
%\author[L.\ Krenz, L.\ Rannabauer, M.\ Bader]{Lukas Krenz, Leonhard Rannabauer and Michael Bader}
\author[Krenz, Rannabauer, Bader]{Lukas Krenz, Leonhard Rannabauer and Michael Bader}
\date{10th September 2019} 
\institute{Technical University of Munich}

@@

  \item Constant potential temperature (temperature normalized by pressure) with larger, warm bubble and small, cold bubble on top.
  \end{itemize}
    \end{column}~%
    \begin{column}[t]{0.5\textwidth}
      \begin{center}
%        \ifratio{43}{
          %\includegraphics{beamer_43_hydrostatic_equilibrium}
%        } {
          \includegraphics[trim={0 0 0 0.5cm}, clip]{ppam_hydrostatic}
%        }
Background pressure in equilibrium
\end{center}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{Two Bubbles: Simulation}
  \begin{center}
   \ifratio{43}{
%   \movie[width=0.9\textwidth, height=0.466666\textwidth, autostart,, loop, poster]{}{ppam_two_bubbles_cart.ogv}
 } {
   % todo: compute aspect ratio
   %\movie[width=0.5\textwidth, height=0.31891168599\textwidth,autostart,, loop, poster]{}{ppam_two_bubbles_cart.ogv}
   \movie[width=0.6\textwidth, height=0.37571265678449256\textwidth,autostart,loop , poster]{}{ppam_two_bubbles_cart.ogv}
 }
  \end{center}
\end{frame}

@@

\begin{frame}
  \frametitle{AMR vs.\ Fully Refined Grid}
  \begin{block}{Settings}
    \begin{description}
    \item[AMR]
      Mesh with sizes from $\SI{1000/81}{\m} = \SI{12.35}{\m}$ to $\SI{1000/3}{\m} = \SI{333.33}{\m}$.

@@

\begin{frame}
  \frametitle{AMR vs.\ Fully Refined Grid: Grid}
  %  \begin{figure}[h]
  %   \centering
  %   \ifratio{43}{
  %   \movie[width=0.9\textwidth, height=0.6\textwidth, autostart,, loop, poster]{}{two_bubbles_legendre.ogv}
  % }{
  \begin{center}
   \movie[width=0.6\textwidth, height=0.382694023188\textwidth, autostart,, loop, poster]{}{ppam_two_bubbles_leg.ogv}
  \end{center}
  % }
  %   \caption{Two bubbles scenario, with \amr{}}
  % \end{figure}
\end{frame}

\begin{frame}
  \frametitle{AMR vs.\ Fully Refined Grid: Error}
  \begin{figure}[H]
     \centering
%     \ifratio{43}{
% %\includegraphics[width=0.9\textwidth]{thesis_two_bubbles_amr_error}
%   } {
\includegraphics[width=0.55\textwidth]{ppam_two_bubbles_amr_error}
%   }
 \caption*{Potential temperature of fully refined solution minus AMR solution.}
   \end{figure}
\end{frame}

\begin{frame}{3D Cosine Bubble\footfullcite{kelly2012continuous}}
  \begin{columns}
    \begin{column}{0.6\textwidth}
  \begin{center}
    \includegraphics[width=0.85\textwidth]{ppam_cosine_bubble_3d}
  \end{center}
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{itemize}
      \item Polynomial Order 3
      \item $25^3$ cells
      \item Time: \SI{400}{\s}
      \item Viscosity: $\mu = 0.05$
      \end{itemize}
    \end{column}

@@

\begin{frame}
  \frametitle{Shared-Memory Scaling (from\footfullcite{reinarz2019exahype})}
  \begin{center}
  \includegraphics[width=0.4\textwidth]{speedup_tbb}
  \end{center}

>>>>

% https://tex.stackexchange.com/questions/123106/detect-aspect-ratio-in-beamer?noredirect=1&lq=1
\documentclass[aspectratio=169]{beamer}
%\documentclass[aspectratio=43]{beamer}
\usepackage[conference]{beamertheme_tumtalk} % headline and footline
\usepackage{beamercolorscheme_tum} % colorscheme
\usepackage{beamerfontthemestructurebold} % bold headings

@@

@@

\ifratio{43} {
\title[DG w/ AMR for Cloud Simulation]{A High-Order Discontinuous Galerkin Solver with Dynamic Adaptive Mesh Refinement to Simulate Cloud Formation Processes}
} {
\title[High-Order DG with Dynamic AMR to Simulate Clouds]{A High-Order Discontinuous Galerkin Solver with Dynamic Adaptive Mesh Refinement to Simulate Cloud Formation Processes}
}
\subtitle[PPAM]{PPAM 2019}
%\author[L.\ Krenz, L.\ Rannabauer, M.\ Bader]{Lukas Krenz, Leonhard Rannabauer and Michael Bader}
\author[Krenz, Rannabauer, Bader]{Lukas Krenz, Leonhard Rannabauer and Michael Bader}
\date{10th September 2019} 
\institute{Technical University of Munich}

@@

  \item Constant potential temperature (temperature normalized by pressure) with larger, warm bubble and small, cold bubble on top.
  \end{itemize}
    \end{column}~%
    \begin{column}[t]{0.5\textwidth}
      \begin{center}
        \ifratio{43}{
          %\includegraphics{beamer_43_hydrostatic_equilibrium}
          \includegraphics[scale=0.8,trim={0 0 0 0.5cm}, clip]{ppam_hydrostatic}
        } {
          \includegraphics[trim={0 0 0 0.5cm}, clip]{ppam_hydrostatic}
        }
Background pressure in equilibrium
\end{center}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{Two Bubbles: Simulation}
  \begin{center}
   \ifratio{43}{
   \movie[width=0.8\textwidth, height=0.5009502090459902\textwidth,autostart,loop , poster]{}{ppam_two_bubbles_cart.ogv}
 } {
   % todo: compute aspect ratio
   %\movie[width=0.5\textwidth, height=0.31891168599\textwidth,autostart,, loop, poster]{}{ppam_two_bubbles_cart.ogv}
   \movie[width=0.6\textwidth, height=0.37571265678449256\textwidth,autostart,loop , poster]{}{ppam_two_bubbles_cart.ogv}
 }
  \end{center}
\end{frame}

@@

\begin{frame}
  \frametitle{AMR vs.\ Fully Refined Grid}
  \begin{block}{Settings}
    \begin{description}
    \item[AMR]
      Mesh with sizes from $\SI{1000/81}{\m} \approx \SI{12.35}{\m}$ to $\SI{1000/3}{\m} \approx \SI{333.33}{\m}$.

@@

\begin{frame}
  \frametitle{AMR vs.\ Fully Refined Grid: Grid}
  %  \begin{figure}[h]
  %   \centering
  %   \ifratio{43}{
  %   \movie[width=0.9\textwidth, height=0.6\textwidth, autostart,, loop, poster]{}{two_bubbles_legendre.ogv}
  % }{
  \begin{center}
     \ifratio{43}{
   \movie[width=0.8\textwidth, height=0.5102586975840001\textwidth, autostart,, loop, poster]{}{ppam_two_bubbles_leg.ogv}

       } {
   \movie[width=0.6\textwidth, height=0.382694023188\textwidth, autostart,, loop, poster]{}{ppam_two_bubbles_leg.ogv}
   }
  \end{center}
  % }
  %   \caption{Two bubbles scenario, with \amr{}}
  % \end{figure}
\end{frame}

\begin{frame}
  \frametitle{AMR vs.\ Fully Refined Grid: Error}
  \begin{figure}[H]
     \centering
     \ifratio{43}{
\includegraphics[width=0.7\textwidth]{ppam_two_bubbles_amr_error}
   } {
\includegraphics[width=0.55\textwidth]{ppam_two_bubbles_amr_error}
   }
 \caption*{Potential temperature of fully refined solution minus AMR solution.}
   \end{figure}
\end{frame}

\begin{frame}{3D Cosine Bubble\footfullcite{kelly2012continuous}}
  \begin{columns}
    \begin{column}{0.6\textwidth}
  \begin{center}
    \ifratio{43}{
    \includegraphics[width=0.95\textwidth]{ppam_cosine_bubble_3d}
    } {
    \includegraphics[width=0.85\textwidth]{ppam_cosine_bubble_3d}
    }
  \end{center}
    \end{column}
    \begin{column}{0.4\textwidth}
      \begin{itemize}
      \item Polynomial Order 3
      \item $25^3$ cells
      \item Time: \SI{400}{\s}
      \item Viscosity: $\mu = 0.05$
      \end{itemize}
    \end{column}

@@

\begin{frame}
  \frametitle{Shared-Memory Scaling (from\footfullcite{reinarz2019exahype})}
  \begin{center}
    \ifratio{43}{
  \includegraphics[width=0.5\textwidth]{speedup_tbb}
    } {
  \includegraphics[width=0.4\textwidth]{speedup_tbb}
    }
  \end{center}
